A decentralized network support middleware for MMOGs

### 2009-09-09 textos/PlanoDoutorado/Lugano/planodoc_lugano.tex

\item Design techniques and algorithms that aim to reduce intra-server and server-client communication, in order to save resources of the server nodes, reduce delays in the communication between them and expand the audience of the game due to the reduction in the bandwidth required to play it and, besides, reducing the requirements for a computer to be part of the server system, without undermining the game experience of the players;

>>>>

\item Design techniques and algorithms that aim to reduce inter-server and server-client communication, in order to save resources of the server nodes, reduce delays in the communication between them and expand the audience of the game due to the reduction in the bandwidth required to play it and, besides, reducing the requirements for a computer to be part of the server system, without undermining the game experience of the players;
